Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-02 ms_pre_post.Rmd
Finish first introductory paragraph

<!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the viabilities and genotypes of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].

<!--- TODO: PARAGRAGH ON EVOLUTION OF PRE-COPULATORY INBREEDING AVOIDANCE --->

<!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->

>>>>

<!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016]. For example, the frequency at which a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016]. Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates [@Parker1983 @Parker2006], such as when focal females mate multiply (i.e., polyandry) to avoid inbreeding [e.g., @Mays2008; @Brouwer2011; @Kingma2013; @Duthie]. Mate choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes affecting mating frequency and pre-copulatory and post-copulatory inbreeding avoidance. However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance jointly evolve, meaning that there are no formal hypotheses for predicting which of these reproductive decisions should arise across different biological systems.

<!--- TODO: PARAGRAGH ON INBREEDING, PRE-COP, AND POST-COP AVOIDANCE --->
